Early stopping in an animal study

### 2024-06-19 text/04/early-stopping-animal.Rmd
Update 2004 files

---
title: Early stopping in an animal study
author: Steve Simon
date: 2004-07-01
categories:
- Blog post
tags:
- Early stopping
output: html_document
---

>>>>

---
title: Early stopping in an animal study
author: Steve Simon
date: 2004-07-01
categories:
- Blog post
tags:
- Early stopping
output: html_document
page_update: partial
---
